Supplementary materials: Reproducibility of SNV-calling in multiple sequencing runs from single tumors

### 2015-11-23 PAPER/Supplementary.tex
finished edits to Supplementary (captions)

\section{Figures}

%% Figure 2
\begin{figure}
\centerline{
\includegraphics[width=5in]{orig_Figure3.pdf} }
\caption{\textbf{One third (WGA) to one half (WGS) of putative SNVs were recovered in technical replicates.} Density of the percentage of each WGS (blue) and WGA (red) sample that is present in the overlap between replicates for each patient. The WGS distribution is higher and narrower, showing that the WGS samples overall have a higher percentage overlap than the WGA samples, and less range in this parameter.}
\label{fig:density}
\end{figure}

\section{Tables}

>>>>

%\section{Figures}

%% Figure 2
\begin{figure}
\centerline{
\includegraphics[width=5in]{FigureS1.pdf} }
\caption{\textbf{One third (WGA) to one half (WGS) of putative SNVs were recovered in technical replicates.} Density of the percentage of each WGS (green) and WGA (orange) sample that is present in the overlap between replicates for each patient. The WGS distribution is higher and narrower, showing that the WGS samples overall have a higher percentage overlap than the WGA samples, and less range in this parameter.}
\label{fig:density}
\end{figure}

\begin{figure}
\centerline{
\includegraphics[width=5in]{FigureS2.pdf} }
\caption{\textbf{Number of putative SNVs in a sample does not correlate with coverage.} The number of SNVs called in a sample does not correlate with the coverage of that sample  (Spearman $\rho=-0.13$, $S=671817$, $P=0.12$). While at first glance, it appears that there may be significant separation between WGS and WGA samples along the $y$-axis (WGA samples lie above and below WGS samples), this is not the case because the $y$-axis value (coverage) is an experimental and not a test parameter. It does not impact our results.} 
\label{fig:coverage}
\end{figure}

\begin{figure}
\centerline{
\includegraphics[width=5in]{FigureS3.pdf} }
\caption{\textbf{Number of putative SNVs in a sample does not correlate with percentage of mapped reads.} The number of SNVs called in a sample does not correlate with the percentage of mapped reads in the alignment of that sample  (Spearman $\rho=-0.068$, $S=637326$, $P=0.41$).} 
\label{fig:percent_mapped}
\end{figure}

%\section{Tables}
